On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement

### 2023-10-15 manuscript/sections/results.tex
manuscript: title, keywords, and final touches main text
manuscript: final literature items and formatting

@@

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Portfolio capacity procured by participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
        \label{fig:10-2025-IE-p1-ci_capacity}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{Cost breakdown of a procurement policy.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p1-ci_costandrev}
    \end{subfigure}
    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
    \label{fig:10-2025-IE-p1-ci_procurement}
\end{figure}

@@

\begin{res}
    24/7 CFE procurement mitigates system-level \co \newline 
    emissions through two distinct mechanisms: "profile" and "volume". The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
\end{res}

@@

Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
As for the latter, "excess CFE" might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.

>>>>

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Portfolio capacity procured by participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
        \label{fig:10-2025-IE-p1-ci_capacity}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{Cost breakdown of a procurement policy.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p1-ci_costandrev}
    \end{subfigure}
    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
    \label{fig:10-2025-IE-p1-ci_procurement}
\end{figure}

@@

@@

\begin{res}
    24/7 CFE procurement mitigates system-level \co \newline 
    emissions through two distinct mechanisms: \enquote{profile} and \enquote{volume}. The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
\end{res}

@@

Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour, the \enquote{excess CFE} is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
As for the latter, excess CFE might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.
